# PreProcessing


## The Raw Data

The raw data from zillow contains the following data (desrciptions from the the data page)

* __properties_2016.csv__ - all the properties with their home features for 2016. Note: Some 2017 new properties don't have any data yet except for their parcelid's. Those data points should be populated when properties_2017.csv is available.

* __properties_2017.csv__ - all the properties with their home features for 2017 (released on 10/2/2017)

* __train_2016.csv__ - the training set with transactions from 1/1/2016 to 12/31/2016

* __train_2017.csv__ - the training set with transactions from 1/1/2017 to 9/15/2017 (released on 10/2/2017)

* __sample_submission.csv__ - a sample submission file in the correct format

### Saving Raw Data Using `feather`
The `feather` package provides the ability for very fast read and write of data. For speed purposes we will save all raw data into a `.feather` file format to make all other read faster

```{r save-raw-as-feather, eval=FALSE}
library(feather)
library(readr)

dir.create("data-raw/feather")

prop_16 <- read_csv("data-raw/properties_2016.csv")
prop_17 <- read_csv("data-raw/properties_2017.csv")
train_16 <- read_csv("data-raw/train_2016_v2.csv")
train_17 <- read_csv("data-raw/train_2017.csv")

write_feather(prop_16, "data-raw/feather/properties_2016.feather")
write_feather(prop_17, "data-raw/feather/properties_2017.feather")
write_feather(train_16, "data-raw/feather/train_2016_v2.feather")
write_feather(train_17, "data-raw/feather/train_2017.feather")
```

## Renaming Variables

Many of the feature names are not very consistant. Let's rename them to something easier to work with

### Renaming `properties` Features
```{r prop-rename, warning=FALSE, message=FALSE, eval=FALSE}
library(tidyverse)
library(feather)

prop_16 <- read_feather("data-raw/feather/properties_2016.feather")
prop_17 <- read_feather("data-raw/feather/properties_2017.feather")

prop_16 <- prop_16 %>% 
  rename(
    id_parcel = parcelid,
    build_year = yearbuilt,
    area_basement = basementsqft,
    area_patio = yardbuildingsqft17,
    area_shed = yardbuildingsqft26, 
    area_pool = poolsizesum,  
    area_lot = lotsizesquarefeet, 
    area_garage = garagetotalsqft,
    area_firstfloor_finished_1 = finishedfloor1squarefeet,
    area_firstfloor_finished_2 = finishedsquarefeet50,
    area_living_finished_calc = calculatedfinishedsquarefeet,
    area_base = finishedsquarefeet6,
    area_living_finished = finishedsquarefeet12,
    area_living_perimeter = finishedsquarefeet13,
    area_total = finishedsquarefeet15,  
    num_unit = unitcnt, 
    num_story = numberofstories,  
    num_room = roomcnt,
    num_bathroom = bathroomcnt,
    num_bedroom = bedroomcnt,
    num_bathroom_calc = calculatedbathnbr,
    num_bath = fullbathcnt,  
    num_75_bath = threequarterbathnbr, 
    num_fireplace = fireplacecnt,
    num_pool = poolcnt,  
    num_garage = garagecarcnt,  
    region_county = regionidcounty,
    region_city = regionidcity,
    region_zip = regionidzip,
    region_neighbor = regionidneighborhood,  
    tax_total = taxvaluedollarcnt,
    tax_building = structuretaxvaluedollarcnt,
    tax_land = landtaxvaluedollarcnt,
    tax_property = taxamount,
    tax_year = assessmentyear,
    tax_delinquency = taxdelinquencyflag,
    tax_delinquency_year = taxdelinquencyyear,
    zoning_property = propertyzoningdesc,
    zoning_landuse = propertylandusetypeid,
    zoning_landuse_county = propertycountylandusecode,
    str_flag_fireplace = fireplaceflag, 
    str_flag_tub = hashottuborspa,
    str_quality = buildingqualitytypeid,
    str_framing = buildingclasstypeid,
    str_material = typeconstructiontypeid,
    str_deck = decktypeid,
    str_story = storytypeid,
    str_heating = heatingorsystemtypeid,
    str_aircon = airconditioningtypeid,
    str_arch_style = architecturalstyletypeid
  )

# use 2016 names to rename 17
names(prop_17) <- names(prop_16)

```

### renaming `train` features
```{r train-rename, eval=FALSE}
library(tidyverse)
library(feather)

trans_16 <- read_feather("data-raw/feather/train_2016_v2.feather")
trans_17 <- read_feather("data-raw/feather/train_2017.feather")

trans_16 <- trans_16 %>% 
  rename(
  id_parcel = parcelid,
  date = transactiondate,
  log_error = logerror
  )

# use 2016 names to rename 17
names(trans_17) <- names(trans_16)

```

### Basic Transformations

#### Properties
```{r prop-basic-transform, warning=FALSE, message=FALSE, eval=FALSE}
library(forcats)

prop_16 <- prop_16 %>%
  mutate(
    tax_delinquency = ifelse(tax_delinquency == "Y", "Yes", "No") %>%
      as_factor(),
    str_flag_fireplace = ifelse(str_flag_fireplace == "Y", "Yes", "No") %>%
      as_factor(),
    str_flag_tub = ifelse(str_flag_tub == "Y", "Yes", "No") %>%
      as_factor(),
    zoning_landuse = factor(zoning_landuse, levels = sort(unique(zoning_landuse))),
    zoning_landuse = fct_recode(zoning_landuse,
      "Commercial/Office/Residential Mixed Used" = "31", 
      "Multi-Story Store"                        = "46",
      "Store/Office (Mixed Use)"                 = "47",
      "Duplex (2 Units Any Combination)"         = "246",
      "Triplex (3 Units Any Combination)"        = "247",
      "Quadruplex (4 Units Any Combination)"     = "248",
      "Residential General"                      = "260",
      "Single Family Residential"                = "261",
      "Rural Residence"                          = "262",
      "Mobile Home"                              = "263",
      "Townhouse"                                = "264",
      "Cluster Home"                             = "265",
      "Condominium"                              = "266",
      "Cooperative"                              = "267",
      "Row House"                                = "268",
      "Planned Unit Development"                 = "269",
      "Residential Common Area"                  = "270",
      "Timeshare"                                = "271",
      "Bungalow"                                 = "273",
      "Zero Lot Line"                            = "274",
      "Manufactured Modular Prefabricated Homes" = "275",
      "Patio Home"                               = "276",
      "Inferred Single Family Residential"       = "279",
      "Vacant Land - General"                    = "290",
      "Residential Vacant Land"                  = "291"
      )
    )

prop_17 <- prop_17 %>%
  mutate(
    tax_delinquency = ifelse(tax_delinquency == "Y", "Yes", "No") %>%
      as_factor(),
    str_flag_fireplace = ifelse(str_flag_fireplace == "Y", "Yes", "No") %>%
      as_factor(),
    str_flag_tub = ifelse(str_flag_tub == "Y", "Yes", "No") %>%
      as_factor(),
    zoning_landuse = factor(zoning_landuse, levels = sort(unique(zoning_landuse))),
    zoning_landuse = fct_recode(zoning_landuse,
      "Commercial/Office/Residential Mixed Used" = "31", 
      "Multi-Story Store"                        = "46",
      "Store/Office (Mixed Use)"                 = "47",
      "Duplex (2 Units Any Combination)"         = "246",
      "Triplex (3 Units Any Combination)"        = "247",
      "Quadruplex (4 Units Any Combination)"     = "248",
      "Residential General"                      = "260",
      "Single Family Residential"                = "261",
      "Rural Residence"                          = "262",
      "Mobile Home"                              = "263",
      "Townhouse"                                = "264",
      "Cluster Home"                             = "265",
      "Condominium"                              = "266",
      "Cooperative"                              = "267",
      "Row House"                                = "268",
      "Planned Unit Development"                 = "269",
      "Residential Common Area"                  = "270",
      "Timeshare"                                = "271",
      "Bungalow"                                 = "273",
      "Zero Lot Line"                            = "274",
      "Manufactured Modular Prefabricated Homes" = "275",
      "Patio Home"                               = "276",
      "Inferred Single Family Residential"       = "279",
      "Vacant Land - General"                    = "290",
      "Residential Vacant Land"                  = "291"
      )
    )

```


#### Transactions
```{r trans-basic-transform, warning=FALSE, message=FALSE, eval=FALSE}
library(lubridate)

# combine transactions into one data frame
trans <- trans_16 %>%
  bind_rows(trans_17) %>%
  mutate(
    abs_log_error = abs(log_error),
    year = year(date),
    month_year = make_date(year(date), month(date)),
    month = month(date, label = TRUE),
    week = floor_date(date, unit = "week"),
    week_of_year = week(date),
    week_since_start = (min(date) %--% date %/% dweeks()) + 1,
    wday = wday(date, label = TRUE),
    day_of_month = day(date)
  )

```


```{r save-output, eval=FALSE}
write_feather(prop_16, "data/properties_16.feather")
write_feather(prop_17, "data/properties_17.feather")
write_feather(trans, "data/transactions.feather")
```


## Extracting Geographic Information

The raw data contains information on block group ids. We can clean this up and use it to bring in external data like Census infomation. 
```{r prop-geo, eval=FALSE}
library(sf)
library(feather)
library(forcats)
library(tidyverse)
library(tidycensus)


# NAD83 / California zone 5 (ftUS)
# https://epsg.io/2229
crs_id <- 2229

api_key <- Sys.getenv("CENSUS_API_KEY")
census_api_key(api_key)

# some obs have no data at all included lat/long
# the original lat / lon are mulitpled by 10e5 so divide to
# get lat lon back when converting to sf
properties <- read_feather("data-raw/properties_2017") %>% 
  filter(!is.na(latitude)) %>%
  mutate(
    lat = latitude / 10e5,
    lon = longitude / 10e5
    ) %>%
  st_as_sf(
    coords = c("lon", "lat"), 
    crs = 4326, # WGS 84
    remove = FALSE # keep lat/long fields
    ) %>%
  st_transform(crs_id)


census_bgs <- get_acs(
  geography = "block group", 
  variables = "B19013_001", 
  state = "CA",
  county = c("Los Angeles", "Orange", "Ventura"), 
  geometry = TRUE, 
  keep_geo_vars = TRUE
  ) %>%
  st_transform(crs_id)

# inner join
# due to lat / lon error some points didn't intersect
# with block groups left = FALSE is inner join
properties_geo <- properties %>%
  st_join(census_bgs, left = FALSE)

# find all of the points that didn't intersect
# buffer them and then join to closest block
# then add back the already joined points
# the buffer distance I just played around with until
# all points joined with a block group
properties_geo <- properties %>%
  filter(!parcelid %in% properties_geo$parcelid) %>%
  st_buffer(dist = 1500) %>% # units are in us-ft based on crs_id
  st_join(census_bgs, left = FALSE, largest = TRUE) %>%
  rbind(properties_geo)


# remove geometry b/c feather can't store lists
properties_geo <- properties_geo %>%
  select(
    id_parcel = parcelid,
    id_geo_state = STATEFP,
    id_geo_county = COUNTYFP,
    id_geo_tract = TRACTCE,
    id_geo_bg = BLKGRPCE,
    id_geo_bg_fips = GEOID,
    id_geo_bg_name = NAME.y,
    geo_bg_arealand = ALAND,
    geo_bg_areawater = AWATER,
    lat, 
    lon
    ) %>%
  mutate(
    id_geo_county_fips = paste0(id_geo_state, id_geo_county),
    id_geo_tract_fips = paste0(id_geo_county_fips, id_geo_tract),
    id_geo_county_name = factor(id_geo_county) %>%
      fct_recode(
        "Los Angeles" = "037",
        "Orange"      = "059",
        "Ventura"     = "111"
      )
  )

# remove geometry b/c feather can't store lists
# add back in when needed from lat lon
properties_geo$geometry <- NULL

write_feather(properties_geo, "data/properties_geo_only.feather")
```